% Created 2017-03-16 四 10:46
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\author{Qiu Wei}
\date{\today}
\title{SVM Experiment Report}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.5.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle
\tableofcontents

\begin{abstract}
This document explains a experiment using libsvm to solve a
k-class classification problem. This experiment used three methods
to decompose a k-class classification problem into several two-class
classification problems. A compare between RBF kernel function and linear
kernal function is also done. This experiment can help us choose the
right decompose method and kernal function when solving k-class
classification problems.
\end{abstract}

\section{Procedure}
\label{sec-1}
I tried three methods to decompose the origin problem: one versus one,
one versus rest and part versus part.

For each two-class classification problem,The parameters are detected using
grid.py which used cross validation and grid search to find the best
parameters. Each class are weighted by the number of instances in the other class.

\subsection{One Versus One Method}
\label{sec-1-1}
The One Versus One Method(OVO) trains $ \frac{k(k-1)}{2} $
models,each model seperates two single classes i and j. When classifying,
the input vector will go through all the models,and each model
will "vote" for their preferred classes. The class with the
most votes will be the result.

\subsection{One Versus Rest Method}
\label{sec-1-2}
The One Versus Rest Method(OVR) trains k models, each model seperates class i and the other
classes.When classifying, the input vector go through all the models and if model i
gave positive result, the input would be classified as class i. If multiple models
tried to classify the input into their classes, the model with the best accuracy would be
considered. If no model reacted, the input would be grouped in class -1.

\subsection{Part Vesus Part Method}
\label{sec-1-3}
The Part Vesus Part Method(PVP) uses a technical inspired by binary search algorithm.
The first model divides the classes into two parts with similar number of classes.
After going through the first model, the chosen classes will be seperated by the next
model. The possible classes will keep reducing until only one class is left. This method
uses a total number of approximate n models for classifying.
\section{Result}
\label{sec-2}
\begin{center}
\begin{tabular}{lll}
\hline
Method & Kernal Function & Accuracy\\
\hline
OVO & RBF & 72.5891677675033 \%\\
OVR & RBF & 65.85204755614267 \%\\
PVP & RBF & 69.48480845442536 \%\\
OVO & Linear & 63.14398943196829 \%\\
OVR & Linear & 42.40422721268164 \%\\
PVP & Linear & 54.359313077939234 \%\\
\hline
\end{tabular}
\end{center}
\section{Analyse}
\label{sec-3}
\subsection{Decomposing Method}
\label{sec-3-1}
From the table we can find the OVO method have the best accuracy,the next is PVP
and the worst is OVR.

OVO method gets the best accuracy because it use  $ \frac{k(k-1)}{2} $ models to
vote the most possible choise, and the input of each model is "balanced" : not like
OVR. Whats more, the input of each model is simple so that it's even faster than
other methods when k is not too large. However, if k is very large, OVO will
take too much time to train the models and go through them.

OVR method does not get good accuracy because the input is hard to seperate:
the single class may be too small than the rest classes. And I do not have
a good method to deal with multiple positive results or no positive results.
Though the number of models is less than OVO, each model will cost much more time
to train as the input is the whole trainning set.

PVP method gets a good accuracy and takes less time than OVO.It may be a good choice when
k is large.In this experiment I just divide the classes brutely: in their origin order.
We may get a better result if a smarter dividing method is used.
\subsection{Kernal Function}
\label{sec-3-2}
Linear kernal function get worse accuracy than RBF kernal. It's advantage is less training
time.
\section{Souce Code Explaination}
\label{sec-4}
All the source code are writen in python3.

To run the svm test:
\begin{verbatim}
$ cd src/
$ ./main.py
\end{verbatim}

The program will read the svm models in models/ folder and use it to predict
the test data. If one model is not exist, it will use tools/grid.py to do a grid
search and generate a .model file in models/ folder.

Source code of different decomposing methods can be found in core/ , named
ovo.py, ovr.py and pvp.py.

Util functions can be found in tools/util.py , I put many DSL functions in that file.
% Emacs 24.5.1 (Org mode 8.2.10)
\end{document}